Percussive Synthesizer Generation with Virtual Listeners

### 2020-10-10 templates_aimusic2020/paper.tex
spell &grammar check/table fixes

\section{Virtual Synthesizer Design}
\begin{table}[tb]
\centering
\caption{Synthesizer submodule parameters. $10^{15}$ unique programs are possible. Each synthesizer can contain any number of submodules}
\resizebox{\columnwidth}{!}{\begin{tabular}{ |p{4cm}|p{4cm}|p{4cm}| } 
\hline
Parameters & Value Range & notes and constraints\\
\hline \hline
Attack & 0-3 & A-D-S-R values relative\\
Decay & 0-3 & relative to A-S-R\\
Sustain & 0-3 & relative to A-D-R\\
Release & 0-3 & relative to A-D-S\\
OSC type & sine,square,saw & -\\
IsNoise & boolean & generate noise using \newline cloud of waveform\\
Length & 0-1 second & - \\
StartTime & 0-1 second & Length+Start$<$1\\
Amplitude & 0.1-1 & 1 = max amplitude\\
Pitches(notes) & list of pitches &  range of C0(16.35hz) to B9 \\
HP filter Cutoff & 0-20000hz & -\\
LP filter Cutoff & 20000hz-HP & never lower than HP cutoff\\
Filter Order & 4,8,16 & butterworth filter order \\
\hline
\end{tabular}}

@@

\section{Datasets, Details, and Downloads}
\label{appendix:datasets}
\subsection{Download Instructions}
FreeDB, survey data, and randomly generated sounds can be downloaded from: \url{https://zenodo.org/record/3994999}\\\\
RadarDB requires lengthy downloads and processing. The script for its automated creation can be found under the \enquote{getting\_data} directory of the project:\\
\url{https://github.com/imilas/Synths_Stacks_Search}

\subsection{Details}
Our data sources are a large set of 2 second or shorter drum samples aggregated from personal libraries, free drum kits from the sample-swap project \footnote{https://sampleswap.org/} which we organized into 5 groups, and a large set of drum sounds aggregated from royalty free sources such as music radar \footnote{https://www.musicradar.com/}. We put together 3 databases of drums using these sources. We also created a database of synthetic noise from 1, 3, and 5 stacked virtual synthesizers. Specifications about our datasets can be found in tables~\ref{table:all_db}. We have made our dataset of free-drum sounds available for download. The scripts used to download and process royalty free samples are also made available.

>>>>

\section{Virtual Synthesizer Design}
\begin{table}[tb]
\centering
\caption{Synthesizer submodule parameters. $10^{15}$ unique programs are possible. Each synthesizer can contain any number of submodules}
\resizebox{\columnwidth}{!}{\begin{tabular}{ |>{\centering\arraybackslash}p{4cm}|>{\centering\arraybackslash}p{4cm}|>{\centering\arraybackslash}p{4cm}| } 
\hline
Parameters & Value Range & Notes and Constraints\\
\hline \hline
Attack & 0-3 & A-D-S-R values relative\\
Decay & 0-3 & relative to A-S-R\\
Sustain & 0-3 & relative to A-D-R\\
Release & 0-3 & relative to A-D-S\\
OSC type & sine,square,saw & -\\
IsNoise & boolean & generate noise using \newline cloud of waveform\\
Length & 0-1 second & - \\
StartTime & 0-1 second & Length+Start$<$1\\
Amplitude & 0.1-1 & 1 = max amplitude\\
Pitches(notes) & list of pitches &  range of C0(16.35hz) to B9 \\
HP filter Cutoff & 0-20000hz & -\\
LP filter Cutoff & 20000hz-HP & never lower than HP cutoff\\
Filter Order & 4,8,16 & butterworth filter order \\
\hline
\end{tabular}}

@@

\section{Dataset Details and Downloads}
\label{appendix:datasets}
\subsection{Download Instructions}
FreeDB, survey data, and randomly generated sounds can be downloaded from: \url{https://zenodo.org/record/3994999}\\\\
RadarDB requires lengthy downloads and processing. The script for its automated creation can be found under the \enquote{getting\_data} directory of the project:\\
\url{https://github.com/imilas/Synths_Stacks_Search}. 
\\\\
Also included on github is our source-code, models, and extra output examples.

\subsection{Details}
Our data sources are a large set of 2 second or shorter drum samples aggregated from personal libraries, free drum kits from the sample-swap project \footnote{https://sampleswap.org/} which we organized into 5 groups, and a large set of drum sounds aggregated from royalty free sources such as music radar \footnote{https://www.musicradar.com/}. We put together 3 databases of drums using these sources. We also created a database of synthetic noise from 1, 3, and 5 stacked virtual synthesizers. Specifications about our datasets can be found in tables~\ref{table:all_db}.
